\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-05-10 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added a sentence about defining FC, CC and MPIF90 in .bashrc or .cshrc

Then, to configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran compiler and MPI package:

>>>>

Then, to configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran compiler and MPI package (another option is to define FC, CC and MPIF90 in your .bash\_profile 
or your .cshrc file):
